---
---

## Solutions {#sol}


### Exercise 1 {#sol1}

Select the MRCs in the Bas-St-Laurent (*reg_id*: 01) and Gaspesie (*reg_id*: 11) regions, then display their 2016 population on a map.

```{r sol1}
mrc_01_11 <- mrc[mrc$reg_id %in% c("01", "11"), ]
plot(mrc_01_11["pop2016"], axes = TRUE)
```

[Return to text](#retour1)

===

### Exercise 2 {#sol2}

Create a map of the MRCs with different fill colors for each region.

```{r sol2}
ggplot(data = mrc_proj, aes(fill = reg_name)) +
    geom_sf()
```

[Return to text](#retour2)

===

### Exercise 3 {#sol3}

a) How many of the forest inventory plots in these regions are affected at each defoliation level?

```{r sol3a}
defo <- st_read("data/tbe2016_gaspe.shp")
plots_defo <- st_join(plots_01_11, defo)
table(plots_defo$level)
```

===

b) Plot the defoliated areas located in the MRC of Kamouraska by severity level, also displaying the MRC border.

```{r sol3b}
mrc_kam <- filter(mrc_01_11, mrc_name == "Kamouraska")
defo_kam <- st_join(defo, mrc_kam, left = FALSE)

ggplot() +
    geom_sf(data = mrc_kam) +
    geom_sf(data = defo_kam, color = NA, aes(fill = level))
```

[Return to text](#retour3)

===

### Exercise 4 {#sol4}

a) Show on a map where the elevation is between 5 and 100 m in the MRC of La Mitis. 

```{r sol4a}
mitis <- filter(mrc_01_11, mrc_name == "La Mitis")
mitis <- st_transform(mitis, st_crs(cdem))

cdem_mitis <- st_crop(cdem, mitis)
plot(cdem_mitis >= 5 & cdem_mitis <= 100)
```

===

b) What is the highest elevation in that MRC?

```{r sol4b}
cdem_mitis_vals <- cdem_mitis[[1]]
max(cdem_mitis_vals, na.rm = TRUE)
```

[Return to text](#retour4)
